\LARGE \bf A Pipeline to Assemble Near-Accident Footage Datasets

### 2020-10-07 paper.tex
Added by-class histogram

\documentclass[letterpaper, 10 pt, conference]{IEEEconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[style=ieee]{biblatex}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots}

@@

\todo{Write the METHODOLOGY}
\begin{itemize}
  \item Major pipeline
  \item Presenting a graph or figure of the pipeline architecture
  \begin{itemize}
    \item pre-processing
    \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
    \item Blurring (tracking and blurring of vehicle plates and faces)
  \end{itemize}
\end{itemize}
\subsection{Video Preprocessing}
\subsection{Automatic Annotation}
\subsection{Object Detection \& Tracking}
\subsection{Blurring}

@@

>>>>

\documentclass[letterpaper, 10 pt, conference]{IEEEconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[style=ieee]{biblatex}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}

@@

\todo{Write the METHODOLOGY}
\begin{itemize}
  \item Major pipeline
  \item Presenting a graph or figure of the pipeline architecture
  \begin{itemize}
    \item pre-processing
    \item Tracking we can mention how prepare to solve the tracking problem (challenge and future work)
    \item Blurring (tracking and blurring of vehicle plates and faces)
  \end{itemize}
\end{itemize}
\tikzset{
    module/.style={%
        draw, rounded corners,
        minimum width=#1,
        minimum height=7mm,
        font=\sffamily
        },
    module/.default=2cm,
    >=LaTeX
}
\begin{tikzpicture}[
  % This will show the frame around the figure
  show background rectangle]

  % Place first 6 items
  \node[module] (crawler) {Web-Scrapers};
  \node[module, below=of crawler] (downloader) {Downloaders};
  \node[module, below=of downloader] (splitter) {Video-Splitter};
  \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
  \node[module, below=of labeller] (face-blur) {Face Blurring};
  \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
  \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
  \node[anchor=north west,inner sep=1pt] at (anon.north west) 
    {Anonymization};
  \node[module, below=of anon] (uploader) {Data-Uploader};
  \draw[->] (crawler)--(downloader);
  \draw[->] (downloader)--(splitter);
  \draw[->] (splitter)--(labeller);
  \draw[->] (labeller)--(face-blur);
  \draw[->] (face-blur)--(license-blur);
  \draw[->] (license-blur)--(uploader);

\end{tikzpicture}
\subsection{Video Preprocessing}
\subsection{Automatic Annotation}
\subsection{Object Detection \& Tracking}
\subsection{Blurring}

@@

\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Objects by class},
  xlabel={Class},
  ylabel={Frequency (\# of bounding boxes)},
  xtick=data,
  xticklabels from table={\byclass}{X}
]
\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
\end{axis}
\end{tikzpicture}
\end{center}
